---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# droneland

<!-- badges: start -->
[![R-CMD-check](https://github.com/softloud/droneland/workflows/R-CMD-check/badge.svg)](https://github.com/softloud/droneland/actions)
<!-- badges: end -->

The goal of droneland is to calculate the area of land captured by a drone image, using the method outlined in this [manuscript](https://www.tandfonline.com/doi/full/10.1080/01431161.2017.1280639).

Why do we care? Because ecological abundance is modelled using observed animeeple / land area. 

## Installation

You can install the development version from [GitHub](https://github.com/):

``` r
# install.packages("devtools")
devtools::install_github("softloud/droneland")
```

## Example

Suppose we have a drone image of 7952 x 5304 pixels taken from 200 metres with a camera angled at 25 degrees with a vertical field of view of 38 degrees and a horizontal field of view of 54 degrees. Then the area of land captured, in metres, is

```{r}
library(droneland)

drone_image_area(
  camera_angle = 25,
  vertical_fov = 38,
  horizontal_fov = 54,
  height = 200,
  pixel_row = 7952,
  pixel_col = 5304
)

# dimensions of trapezoid

drone_image_area(
  camera_angle = 25,
  vertical_fov = 38,
  horizontal_fov = 54,
  height = 200,
  pixel_row = 7952,
  pixel_col = 5304,
  dim = TRUE
) %>% purrr::map(round)


```


## Diagrams of angles and derivations

Check [my derivations](https://www.overleaf.com/read/twnpsndycrgw), please and thank you :) 

In the derivations there are diagrams to check what angles to input. 

## Cite this package

```{r}
citation("droneland")

```

